Waggle dance distributions quantify collective foraging in honey bee colonies: Supplementary material

### 2022-04-05 analysis/manuscript/supplementary_material.Rmd
updated SI docs. Need to rerun as CAD looking odd

library(dplyr)
library(kableExtra)
library(flextable)
library(tibble)
library(purrr)

@@

plots <- map(all_sites, 2)
plots <- plots %>%
  map(
    ~ {.x + theme(
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    )}
  )
print(plots$BEL)

plot_grid(plotlist = plots, nrow = 5)

```

@@

# load fit data
load("results/site_fit_results.Rdata")

>>>>

library(dplyr)
library(kableExtra)
library(flextable)
library(tibble)
library(purrr)
library(gridExtra)

@@

plots <- map(all_sites, 2)
plots <- plots %>%
  map(
    ~ {
      .x + theme(
        axis.title.x = element_blank(),
        axis.title.y = element_blank()
      )
    }
  )

allsites_plot <- plot_grid(
  plotlist = plots, nrow = 5,
  hjust = -0.1, label_x = 0.7,
  labels = names(plots)
)
y.grob <- textGrob(
  "cumulative frequency",
  gp = gpar(),
  rot = 90
)
x.grob <- textGrob(
  "waggle run duration (s)",
  gp = gpar()
)

# add to plot
grid.arrange(arrangeGrob(allsites_plot, left = y.grob, bottom = x.grob))
```

@@
